Analyzing Trends in U.S. Residential Real Estate Prices

### 2024-04-14 outputs/paper/paper.qmd
paper updated

---
title: "TBD"
subtitle: "TBD"
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: https://github.com/iJustinn/House_Price.git"
date: today
date-format: long
abstract: "TBD"
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Analyzing Trends in U.S. Residential Real Estate Prices"
subtitle: "A Data-Driven Approach to Understand the Market"
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: https://github.com/iJustinn/House_Price.git"
date: today
date-format: long
abstract: "This research explores the dynamics of the U.S. housing market. It provides a comprehensive analysis of price trends across different states and housing types, revealing significant escalations in recent years. The study elucidates how location, property characteristics, and external economic factors influence house prices."
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---
